\documentclass[line,margin]{res}

\makeatletter
\def\@classoptionslist{line}
\makeatother

\usepackage[letterpaper,margin=1in]{geometry}
\usepackage[scaled]{helvet}
\usepackage{url}
\usepackage{hyperref}
\usepackage{ragged2e}
\usepackage{multicol}

\renewcommand{\familydefault}{\sfdefault}
\renewcommand{\sectionfont}{\bf\rmfamily}

\headheight=12pt
\headsep=40pt
\addtolength{\textheight}{20pt}
\topmargin=-1in
\resumewidth=6.5in
\addtolength{\resumewidth}{-\sectionwidth}
\textwidth=\resumewidth

\newlength{\tablewidth}
\setlength{\tablewidth}{\resumewidth}
\addtolength{\tablewidth}{\sectionwidth}
\addtolength{\tablewidth}{8pt}

\begin{document}

\hspace{-\sectionwidth}\hspace{-4pt}
\begin{tabular*}{\tablewidth}{@{\extracolsep{\fill} } l r }
  \parbox[b]{10cm}{{\Huge\bf\rmfamily Christopher Cooper}\vspace{3pt}\\
  1709 Western Dr, West Lafayette, IN 47906}
  & \begin{minipage}[b]{6cm}
    \begin{flushright}
      %% \rmfamily
      (765) 233-6222\\
      \href{http://cg505.github.io}{\ttfamily cg505.github.io}\\
      \href{mailto:christopher.c.cooper@gmail.com}{christopher.c.cooper@gmail.com}
    \end{flushright}
  \end{minipage}
  %% \moveleft.5\hoffset\centerline{1985 Storm Lane}
  %% \moveleft.5\hoffset\centerline{Troy, NY 12180}
  %% \moveleft.5\hoffset\centerline{(518) 273-0014 or (518) 272-6666}
\end{tabular*}


\begin{resume}
% \vfill

  \section{OBJECTIVE}
  To obtain experience in the professional workplace developing production applications.


  \section{EDUCATION}
  {\bf\rmfamily West Lafayette High School}\hfill Fall 2012 -- present\\
  Pursuing a Core 40 Diploma with Academic Honors, expected May 2016\\
  Current GPA: 4.0 with 53 credits completed, 6 in progress, including 17 AP credits\\
  Relevant Coursework:
  \multicolsep 0pt
  \begin{multicols}{2}
  \begin{itemize} \itemsep -2pt\RaggedRight
  \item AP Calculus BC
  \item AP Physics C
    \columnbreak
  \item AP Computer Science test
  \end{itemize}
  \end{multicols}

  {\bf\rmfamily Purdue University, West Lafayette}\hfill Fall 2014 -- Fall 2015\\
  Non-degree seeking undergraduate student during high school\\
  GPA: 4.0 with 11 credit-hours in 3 courses \\
  Coursework:
  \multicolsep 0pt
  \begin{multicols}{2}
  \begin{itemize} \itemsep -2pt
  \item Honors multivariate calculus
  \item Linear algebra
  \item Proof-based analysis
  \end{itemize}
  \end{multicols}

  % {\bf\rmfamily Undetermined university}\hfill Planned enrollment fall 2016\\
  % Pursuing a Bachelor's in Computer Science\\


  \section{EXPERIENCE}
  {\bf\rmfamily American Computer Science League Chapter, West Lafayette High School}\\
  \emph{President}\hfill Spring 2015 -- present\\
  Previously Vice President\hfill Spring 2013 -- Spring 2015\\
  Previously Member\hfill Fall 2012 -- Spring 2013
  \begin{itemize}  \itemsep -2pt % reduce space between items
  \item Taught programming and computer science concepts to about 20 members.
  \item Won first place in a five-state regional computer science competition.
  % \item Shared responsibility with three other leaders to organize regular meetings.
  \end{itemize}

  {\bf\rmfamily DevilTech Zero Robotics Team, West Lafayette High School}\\
  \emph{Team Lead and Programmer}\hfill Fall 2014 -- Winter 2015
  \begin{itemize}  \itemsep -2pt % reduce space between items
  \item Wrote C/C++ code for autonomous robots aboard the International Space Station.
  % \item Organized meeting schedule and educational materials for 10+ members.
  \item Worked closely with other Zero Robotics teams from around the world.
  \item Placed third in an international competition.
  \end{itemize}

  {\bf\rmfamily  Westside Boiler Invasion Robotics, West Lafayette High School}\\
  \emph{Programmer}\hfill Fall 2012 -- Spring 2015
  \begin{itemize}  \itemsep -2pt % reduce space between items
  \item Worked in a small team to design and develop the team's website using Rails.
  \item Created a system for scouting potential alliance partners using C and node-webkit.
  \end{itemize}

  %% {\bf\rmfamily Sound of West Side Marching Band, West Lafayette High School}\\
  %% \emph{Woodwind Co-captain}\hfill Fall 2014 \& 2015\\
  %% Previously Member\hfill Fall 2012 \& 2013
  %% \begin{itemize}  \itemsep -2pt % reduce space between items
  %% \item Performed with the band, making the top sixteen in the state two different years.
  %% \item Lead a section of about 25 musicians along with one other co-captain.
  %% \end{itemize}


  %% \section{OTHER EXPERIENCE}
  %% Westside Boiler Invasion Robotics Team\hfill 2012 -- present\\
  %% West Lafayette Debate Team\hfill 2013 -- present\\
  %% West Lafayette High School Jazz and Concert Bands\hfill 2012 -- present\\
  %% West Lafayette Jr/Sr High School MathCounts Team Member\hfill 2011 -- 2012


  \section{SKILLS}
  {\bf\rmfamily Programming Languages}
  \begin{itemize} \itemsep -2pt
  \item \emph{Proficient}: Lisp, Ruby, C, HTML, CSS
  \item \emph{Familiar}: C++, Javascript, Java
  \end{itemize}

  {\bf\rmfamily Other Tools}
  \begin{itemize} \itemsep -2pt
  \item \emph{Proficient}: GNU/Linux and shell utilities, git, GNU Emacs, \LaTeX
  \item \emph{Familiar}: Ruby on Rails, SQL, Bash/Zsh
  \end{itemize}

  % {\bf\rmfamily Mathematics} \quad
  % Solid knowledge of college-level mathematics and understanding of applications to the sciences.

  %% {\bf\rmfamily Sciences} \quad
  %% Developed understanding of high-school physics, biology, and chemistry.

  %% {\bf\rmfamily Speaking} \quad
  %% Considerable experience with public speaking and argumentation.

  %% {\bf\rmfamily Music} \quad
  %% Proficiency on saxophone, as well as a good understanding of music theory.


  \section{HONORS}
  %% Tony Zamora Jazz Scholarship Winner\hfill 2016\\
  \$8000/yr Purdue Presidential Scholarship Winner\hfill 2016\\
  Tony Zamora Jazz Scholarship Wiiner\hfill 2016\\
  Purdue Bands Leath Scholarship Winner\hfill 2016\\
  American Computer Science League Central Divison Senior Level Winner\hfill 2015\\
  Zero Robotics International Third Seed Alliance\hfill 2015\\
  % AP Scholar with Honor\hfill 2015\\
  National Speech and Debate Association National Tournament Qualifier\hfill 2015\\
  Indiana High School All-State Jazz Band Lead Alto/Tenor\hfill 2014 \& 2015\\
  American Invitational Mathematics Examination Qualifier\hfill 2012 \& 2014
  % American Mathematics Competition School Top 10 Scorer\hfill 2012\\
  % Lafayette Kiwanis Club Scholarship Award Winner\hfill 2012

% \vfill\vfill
\end{resume}

\end{document}
